\begin{abstract}
Cloud network providers continuously enhance the capability to meet the increasing demands from both users and operators. On one hand，the emerging cloud network users have differentiated requirements for network services. In addition to the bandwidth and cost, users recently have more stringent requirements on the end-to-end path quality for specified Internet traffic flows. On the other hand, the high expense of data transferred across Internet peering edges requires effective optimal routing through software-defined WAN networks. However, these operations introduce high complexity for the modern centralized traffic management in control plane, which need to find routes for $O(10^{10})$ flows in 10 seconds. 

To deal with the increased scale, we propose {\sys}, a platform supporting traffic management with regard to both backbond and Internet workloads. Three key optimizations in system architecture, control, and data planes by offering tiered cloud network services based on users' requirements. First, {\sys} leverages a hybrid architecture of commodity routers and software routers to monitor performance across policy-compliant route choices for each application request instead of destination, at line rate and with a small memory footprint. Second, we introduce high-performance egress traffic scheduling through joint operation for both Internet and backbone networks. Last, we address the hard problem of routing compression at the data plane to support large-scale routing in cloud-scale fine-grained routing. The evalution over network with 16 PoPs have shown that {\sys} is able to find the routes for 1 billiones flows within 10 seconds, and improve the delay of 67\% performance-aware flows. 
\end{abstract} 
